Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-23 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
adding images

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/classroom-maps-axes-annotation.png}
  \caption{The top two images show the Player/Stage classroom simulations used in the example, with the base on the left and the target on the right. The desks are simulated as red boxes, and the chalkboard and lectern (where present) as blue and green boxes respectively. Furthermore, the solid green line in the base connects the boundary points of the front of the room. The lower two images show the metric and place maps generated by Dora during the example runs.}
  \label{fig:dora-maps}
\end{figure}

>>>>

\begin{figure*}[t]
  \includegraphics[width=\textwidth]{images/worked-example.png}
  \caption{\textbf{TODO}}
  \label{fig:rooms-and-pic}
\end{figure*}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{\textbf{TODO}}
  \label{fig:rooms}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/ug40.png}
  \caption{\textbf{TODO}}
  \label{fig:ug40}
\end{figure}
